\listfiles
\documentclass[12pt]{report}  %%% Changed from 12pt. Fixed dimensions
                              %%% have not been updated
%%%%
%%nomenclature hack from http://www.freiheitsfreund.de/2010/10/24/automatically-run-makeindex-from-within-a-latex-document-with-write18/%%%

\usepackage[intoc]{nomencl}

\textwidth=6in \oddsidemargin=0.2in \topmargin=-0.5in
\textheight=9in  % 9in must include page numbers
\textfloatsep = 0.4in \addtocontents{toc}{\vspace{0.4in} \hfill
Page\endgraf} \addtocontents{lof}{\vspace{0.2in} \hspace{0.13in} \
Figure\hfill Page\endgraf} \addtocontents{lot}{\vspace{0.2in}
\hspace{0.13in} \ Table\hfill Page\endgraf}

\usepackage{textcomp}
\usepackage{array}
\usepackage{listings}
\usepackage{setspace}
\usepackage{mathptmx}
\usepackage[table, svgnames]{xcolor}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{amssymb, amsmath}
\usepackage{subfig}
\usepackage{epsfig}
\usepackage{times}
\usepackage{float}
\usepackage{rotating}
\usepackage{makeidx}
\usepackage{url}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[subfigure, titles]{tocloft}
\usepackage{acronym}
\usepackage{datetime}
\usepackage{gensymb}
\usepackage{epigraph}



%%another algorithm package
\usepackage{algorithm}
\usepackage{algorithmic}

\renewcommand{\nomname}{LIST OF ABBREVIATIONS}
\makenomenclature

% New command: caption for name
\newcommand\tline[2]{$\underset{\text{#1}}{\text{\underline{\hspace{#2}}}}$}

% New command: change margin for dedication
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\graphicspath{{images/}}
\DeclareGraphicsExtensions{.pdf, .jpeg, .png, .PNG, .jpg, .eps, .tiff}

\urlstyle{same}

\usepackage{makecell}
\usepackage{titletoc}
\usepackage{style/sfchap}
\usepackage{style/sfsection}
\usepackage[authoryear]{natbib}
%\usepackage{apacite}
\usepackage{appendix}
%\usepackage{tocbibind}
\usepackage{tabularx}
\usepackage[nottoc]{tocbibind}

% Default counter is 7, change to 1 for only sections
\setcounter{secnumdepth}{1}
\setcounter{tocdepth}{1}

\usepackage{hyperref}
\hypersetup{
	pdftitle={Attributes of Brain Functional Network Architecture Supporting Skilled Reading},
	pdfauthor={Stephen Bailey},
	bookmarksnumbered, %Determined if chapter numbers are included in the bookmark list
	pdfstartview={FitH},
	pdfborder={0 0 0},
	plainpages=false
}%
\usepackage[all]{hypcap}

% Stats table label
\newcommand{\statslabel}[2]{\multirowcell{#1}[-1.6mm][c]{#2}}

% Below heading rule.
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

% Prevent double spaced equations
\newenvironment{tightequation}{\singlespace\begin{equation}}{\end{equation}}

% Extra junk to pretty up the table of contents
\setlength{\cftsecnumwidth}{2.8em}
\setlength{\cftsubsecnumwidth}{3.7em}
\setlength{\cftsubsubsecnumwidth}{4.6em}
\setlength{\cftparanumwidth}{5.5em}
\setlength{\cftsubparanumwidth}{6.5em}
\setlength{\cfttabnumwidth}{3.5em}
\setlength{\cftfignumwidth}{3.5em} 

\renewcommand{\contentsname}{TABLE OF CONTENTS}
\renewcommand{\listfigurename}{LIST OF FIGURES}
\renewcommand{\listtablename}{LIST OF TABLES}
\renewcommand{\bibname}{ \texorpdfstring{{BIBLIOGRAPHY\vspace{10mm}}}{BIBLIOGRAPHY}   }
%
\renewcommand{\chaptermark}[1]{%
  \markboth{\MakeUppercase{%
      \chaptername}\ \thechapter.%
    \ #1}{}}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
    
\interfootnotelinepenalty=10000 %prevents the splitting of long footnotes across multiple pages. Use with caution. 

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Prevent the warning: pdfTeX warning (ext4): destination with the same identifier (name{page.1}) has been already used, duplicate ignored
%%	This setting will make a difference to the output because the page number is suppressed for the title page
\pagenumbering{alph}

\begin{titlepage}
\thispagestyle{empty}\enlargethispage{\the\footskip}%
\begin{center}
	{\setstretch{1.66} \textsc{Attributes of Brain Functional Network Architecture\\ Supporting Skilled Reading}}\par%
	\vskip.5in
	By
	\vskip .4in
	{Stephen K. Bailey}
	\vskip .4in
	
	\begin{doublespace}
	Dissertation\\
		Submitted to the Faculty of the \\
		Graduate School of Vanderbilt University \\
		in partial fulfillment of the requirements \\
		for the degree of \\ [.2in]
	\end{doublespace}
	
	\textsc{Doctor of Philosophy} \\[.2in]
	in \\[.15in]
	\textsc{Neuroscience} \\[.25in]
	December 15, 2018 \\[0.1in]
	Nashville, Tennessee
	\vskip .5in
\end{center}
%%%Uncomment for Signatures%%%
\hspace*{0.3in} Approved: \hskip 3.4in Date:\\[1em]
% \hspace*{1.0in} \rule{3.0in}{.5pt} \hskip 0.1in \rule{1in}{.5pt} \\[.1in]
% \hspace*{1.0in} \rule{3.0in}{.5pt} \hskip 0.1in \rule{1in}{.5pt} \\[.1in]
% \hspace*{1.0in} \rule{3.0in}{.5pt} \hskip 0.1in \rule{1in}{.5pt} \\[.1in]
% \hspace*{1.0in} \rule{3.0in}{.5pt} \hskip 0.1in \rule{1in}{.5pt} %\\[.1in]

\hspace*{0.05in} \tline{Professor Adam Anderson \hspace*{2.6in}}{4.0in} \hskip 0.1in  \tline{}{1.0in} \\[.25in]
\hspace*{.3in} \tline{Professor Laurie Cutting \hspace*{2.7in}}{4.0in} \hskip 0.1in  \tline{}{1.0in} \\[.25in]
\hspace*{0.3in} \tline{Professor Zhaohua Ding \hspace*{2.71in}}{4.0in} \hskip 0.1in \tline{}{1.0in} \\[.25in]
\hspace*{0.3in} \tline{Professor Gavin Price \hspace*{2.83in}}{4.0in} \hskip 0.1in \tline{}{1.0in} 

%%%%%%%%%%%%%%
%%%%%%Uncomment  for Approved Names%%%%%%
% \begin{center}
% \begin{doublespace}
% Approved:\\
% \hspace*{1.0in} Professor Laurie Cutting \\

% Professor Adam Anderson \\
% Professor Zhaohua Ding \\
% Professor Gavin Price  \\
% \end{doublespace}
% \end{center}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\doublespacing
\pagenumbering{roman} \setcounter{page}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{DEDICATION}
\addcontentsline{toc}{chapter}{DEDICATION}
\vspace{7mm}

\begin{changemargin}{1in}{1in} 
    This work -- and especially the years of learning it is built upon -- is dedicated to my parents, Dan and Janine Bailey, who taught me to learn something from everything: novels,  newspapers, comics, classes, car rides, restaurants, sports,   sermons, trivia, movies, games, work, success and failure. Thank you for making the world a place full of meaning.
\end{changemargin} 

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\vspace{7mm}

It is wrong for me to ascribe myself as the sole author of this dissertation. The work described in the following pages is the result of the efforts of dozens of people, most notably my colleagues in Vanderbilt's Education and Brain Sciences Research Laboratory and the participants who lent their time, energy and brains to each of the studies. Julie Delheimer, Lanier Sachs, Laura Barquero, Angela Emerson, Hannah Rowland and Scott Burns worked relentlessly, year upon year, to keep the operations of our busy and growing lab humming along. Their efforts insulated myself and the rest of the research team from the everyday demands of running a high-performing lab, and they made it possible for me to focus almost exclusively on my own research and training. 

I have been privileged to train at an institution rich in resources and funding. The staff at the Imaging Institute, Brain Institute, Kennedy Center and ACCRE have been wonderful colleagues. They were patient with my questions and fumblings as I attempted to play with just about every toy I could get my hands on these past five years. The National Institutes of Health has largely underwritten these experiences, through a variety of mechanisms. These include training grants (T32 MH064913, F31 HD090923), center grants (U54 HD083211), and the many research awards granted to Dr. Cutting (R01 HD044073, R01 HD067254, among others).

I am grateful for a supportive committee that gave me guidance at critical junctures and opened my eyes to a research domains I would not have otherwise seen. Dr. Gavin Price embodied for me the rigor and theoretical drive present in the best of cognitive psychology, and our conversations helped to give a pointed form to many of the ideas explored herein. (Any deviation from clarity is my own.) Dr. Adam Anderson gave me insight into the wider field of biomedical image analysis through his classes and lectures, and he also exposed me to a more programmatic approach to analysis. This move away from GUIs and toolboxes opened me up to new tools and techniques, and it has set me up to be a much more innovative scientist. Finally, my collaborations with Dr. Zhaohua Ding gave me the unique experience of watching a scientific idea evolve from its infancy to its impact, as he chased, teased out, and trumpeted the existence of the BOLD signal in white matter tissue. His tenacity impressed upon me the role grit and sheer hard work play in pushing science forward. 

To Dr. Laurie Cutting I owe a special debt. My experience as a graduate student was unusual: I had all the resources I needed, all the data I could want, all the opportunity I could ask for, from my first day as a student. Dr. Cutting has built a world-class training environment, and she gave me five years of freedom to play in it. What is most impressive to me, though, is that she has fostered a healthy, positive, and professional team culture that has persisted even as the team has turned over and grown. It has been a joy to be a part of this team. I am grateful for the gamble that Dr. Cutting took on me, a prospective student with no background in neuroscience, no experience with imaging, no knowledge of statistics or computing or special education. That I leave with all these things and more is a direct result of the guidance, opportunity and encouragement provided by Dr. Cutting.

I have made too many friends to count or acknowledge, but I will try. My cohort of graduate students -- Mackenzie Catron, Eric Wilkey, David Simon, Dylan Morrow-Jones -- were a great source of encouragement during our first years, as I was scrambling to recover the tiny amount of biochemistry I learned in college and perplexing over $t$-statistics and ANOVA designs. Later support came from my colleagues in the lab, especially Neena Hudson, Stephanie Del Tufo, Tin Nguyen, Mercedes Spencer and Laura Barquero. Then there were those who pulled me away from brains for refreshing moments: Alice Leach, Jake Benzing, Auvy Hossasin and Nausheen Karim. Finally, I must give a special acknowledgment to the very first person I met at Vanderbilt. Katherine Aboud has been a partner and friend in all of my research endeavors -- and later, parenting efforts -- as she pushed me to remember the ``story'' in all of my ``process''. It has been a privilege to study, work and converse with these fine people, and I will miss it greatly. 

The best analogy for the PhD is that of an odyssey: the destination is clear but the path is unknown and treacherous at times. For travelling with me and keeping me grounded, I am grateful for my wife, partner and best friend, Danielle. Our particular journey has been filled with classes and experiments and writing, of course. But it has also been filled with leaky houses, arduous job searches, and, most of all, children. It has only been through her conversation, support, love, and constant reminding of the important things that this odyssey has reached its happy ending.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\singlespacing
\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begingroup
\setlength{\parskip}{1\baselineskip}
\listoftables
\newpage
\listoffigures
\newpage
\printnomenclature
\newpage
\endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\normalsize
\doublespacing
\pagenumbering{arabic}
\setcounter{page}{1}


%% Input your chapter .tex files here.
%% Each one should begin with a call to \chapter{TITLE}
\input{chapters/ch1.tex}
\input{chapters/ch2.tex}
\input{chapters/ch3.tex}
\input{chapters/ch4.tex}
\input{chapters/ch5.tex}
\input{chapters/ch6.tex}

%% Read in nomenclature
\input{chapters/nomenclature.tex}



\singlespacing
\bibliographystyle{apalike}
\bibliography{mendeley.bib}
\end{document}